Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-20 cloneoverflow-latex/cloneoverflow.tex
Small changes. Removed "the first study" from the abstract.

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 31,946
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  Our study is among the first to address the problem of
  outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. The archived dump has a size of 9 gigabytes. The data
dump is in XML format containing information of \textbf{Posts}
(questions and answers) and supporting data such as user accounts and
timestamps of the posts. We were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets which contain 2,347,267 lines
of Java source code excluding comments and blank
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}}.

>>>>

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 31,946
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. The archived dump has a size of 9 gigabytes. The data
dump is in XML format containing information of \textbf{Posts}
(questions and answers) and supporting data such as user accounts and
timestamps of the posts. We were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,347,267
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
% excluding comments and blank lines.
